Design and Implementation of Probabilistic Programming Language Anglican

### 2017-03-05 paper/paper.tex
edits to clarify the different meanings of checkpoint
small further edits for consistency of use of terminology

Upon encountering a checkpoint, the inference algorithm computes
the updated program state and the value to be passed to the
continuation.  How the state is updated, the number of times the
continuation is called, and the value passed to the continuation
of \texttt{sample} depend on the inference algorithm executing
the program.  Section~\ref{sec:inference} provides more detail
on internals of inference algorithms and their interaction with
probabilistic programs.

@@

\texttt{anglican.runtime} is the Anglican runtime library. For
convenience, it exposes common mathematical functions
(\texttt{abs}, \texttt{floor}, \texttt{sin}, \texttt{log},
\texttt{exp}, etc.), but most importantly, it provides
definitions of common distributions. Each distribution object implements a
distribution interface with the \texttt{sample*} and \texttt{observe*} methods;
this interface is defined using Clojure's protocol mechanism
(\texttt{anglican.{\linebreak[0]}runtime/{\linebreak[0]}distribution}).
The \texttt{sample*} \textit{method} returns a random sample and
roughly corresponds to the \texttt{sample} checkpoint.
The \texttt{observe*} \textit{method} returns the log probability
of the value and roughly corresponds to the \texttt{observe}
checkpoint. The methods can be, and sometimes are called from
handlers of the corresponding checkpoints, but do not have to
be. For example, in LMH either the \texttt{sample*} or
the \texttt{observe*} \textit{method} is called for a
\texttt{sample} checkpoint, depending on whether the value is
drawn or reused.

>>>>

Upon encountering a \texttt{sample} or \texttt{observe} record, the
inference algorithm computes the updated program state and the value
to be passed to the continuation.  How the state is updated, the
number of times the continuation is called, and the value passed to
the continuation of \texttt{sample} depend on the inference algorithm
executing the program.  Section~\ref{sec:inference} provides more
detail on internals of inference algorithms and their interaction
with probabilistic programs.

@@

\texttt{anglican.runtime} is the Anglican runtime library. For
convenience, it exposes common mathematical functions
(\texttt{abs}, \texttt{floor}, \texttt{sin}, \texttt{log},
\texttt{exp}, etc.), but most importantly, it provides
definitions of common distributions. Each distribution object implements a
distribution interface with the \texttt{sample*} and \texttt{observe*} methods;
this interface is defined using Clojure's protocol mechanism
(\texttt{anglican.{\linebreak[0]}runtime/{\linebreak[0]}distribution}).
The \texttt{sample*} \textit{method} returns a random sample and
roughly corresponds to the default implementation of the \texttt{sample} checkpoint.
The \texttt{observe*} \textit{method} returns the log probability
of the value, which roughly corresponds to the default implementation of the \texttt{observe}
checkpoint. The methods can be, and sometimes are called from
handlers of the corresponding checkpoints, but do not have to
be. For example, in LMH either the \texttt{sample*} or
the \texttt{observe*} \textit{method} is called for a
\texttt{sample} checkpoint, depending on whether the value is
drawn or reused.
